---
title: "Machine Learning - Final project (project 10)"
author: "Bazile Cédric and Jain Khushi"
format: pdf
editor: visual
---

```{r}
#Libraries
here::i_am("Dauphine-ML-project-2024-2025.Rproj")
library(here)
library(readr)

## Data management
library(dplyr)
library(tidyr)
library(data.table)
library(stringr)


## Graphics libraries
library(ggplot2)
library(scales)
library(plotly)

## ML
library(torch)
```

## Introduction

## Cleaning phase

```{r}
#Learning data set

## Import data
learn_df <- read_csv("Data - source/project-10-files/learn_dataset.csv")

##Check for NA
learn_df %>%  summarise_all(~ sum(is.na(.))) # No missing data

# Test dataset
## Import data
test_df <- read_csv("Data - source/project-10-files/learn_dataset.csv")
any(duplicated(learn_df$KEY_PRIMARY)) 

##Check for NA
test_df %>%  summarise_all(~ sum(is.na(.))) # No missing data
any(duplicated(test_df$KEY_PRIMARY)) 
```

The principal datasets, both from the learning and testing phases, do not contain missing values or duplicates. However, as indicated in the instructions, a large number of missing values exist when adding the additional data on retirement, sports, and jobs.

```{r Create_the_dataframe_learning_data}

# Import additional data

learn_emp_type <- read_csv("Data - source/project-10-files/learn_dataset_emp_type.csv")

learn_job <- read_csv("Data - source/project-10-files/learn_dataset_job.csv")

learn_retired_former <- read_csv("Data - source/project-10-files/learn_dataset_retired_former.csv")

learn_retired_jobs <- read_csv("Data - source/project-10-files/learn_dataset_retired_jobs.csv")

learn_retired_pension <- read_csv("Data - source/project-10-files/learn_dataset_retired_pension.csv")

learn_sport <- read_csv("Data - source/project-10-files/learn_dataset_sport.csv")

# Chekcing for duplicate
 
any(duplicated(learn_emp_type$KEY_PRIMARY))
any(duplicated(learn_job$KEY_PRIMARY))
any(duplicated(learn_retired_former$KEY_PRIMARY))
any(duplicated(learn_retired_jobs$KEY_PRIMARY))
any(duplicated(learn_retired_pension$KEY_PRIMARY))
any(duplicated(learn_sport$KEY_PRIMARY))
# No duplicates found

# Merger with left join
learn_merged <- learn_df %>%
  left_join(learn_emp_type, by = "PRIMARY_KEY") %>%
  left_join(learn_job, by = "PRIMARY_KEY") %>%
  left_join(learn_retired_former, by = "PRIMARY_KEY") %>%
  left_join(learn_retired_jobs, by = "PRIMARY_KEY") %>%
  left_join(learn_retired_pension, by = "PRIMARY_KEY") %>%
  left_join(learn_sport, by = "PRIMARY_KEY")

# Suppression of the suffix .x and .y
learn_merged <- learn_merged %>%
  rename_with(~ str_remove(., "\\.x$|\\.y$"))

```

```{r Create_the_dataframe_test_data}

# Import additional data

test_emp_type <- read_csv("Data - source/project-10-files/test_dataset_emp_type.csv")

test_job <- read_csv("Data - source/project-10-files/test_dataset_job.csv")

test_retired_former <- read_csv("Data - source/project-10-files/test_dataset_retired_former.csv")

test_retired_jobs <- read_csv("Data - source/project-10-files/test_dataset_retired_jobs.csv")

test_retired_pension <- read_csv("Data - source/project-10-files/test_dataset_retired_pension.csv")

test_sport <- read_csv("Data - source/project-10-files/test_dataset_sport.csv")

# Chekcing for duplicate
 
any(duplicated(test_emp_type$KEY_PRIMARY))
any(duplicated(test_job$KEY_PRIMARY))
any(duplicated(test_retired_former$KEY_PRIMARY))
any(duplicated(test_retired_jobs$KEY_PRIMARY))
any(duplicated(test_retired_pension$KEY_PRIMARY))
any(duplicated(test_sport$KEY_PRIMARY))
# No duplicates found

# Merger with left join
test_merged <- test_df %>%
  left_join(test_emp_type, by = "PRIMARY_KEY") %>%
  left_join(test_job, by = "PRIMARY_KEY") %>%
  left_join(test_retired_former, by = "PRIMARY_KEY") %>%
  left_join(test_retired_jobs, by = "PRIMARY_KEY") %>%
  left_join(test_retired_pension, by = "PRIMARY_KEY") %>%
  left_join(test_sport, by = "PRIMARY_KEY")


```

```{r NA_tables}

# List of the column of the main dataset : this list will be used to keep only columns of the additional dataset in order to see the number and frequency of NA
learn_original_columns <- colnames(learn_df)
test_original_columns <- colnames(test_df)

# Learning set : Number of NA for each column
learn_na_count <- learn_merged %>%
  select(-all_of(learn_original_columns)) %>%  
  summarise(across(everything(), ~ as.integer(sum(is.na(.))))) %>%
  mutate(Statistics = "Learning set : count")  # Addition of a column to name the created statistics

# Learning set : % of NA for each colummn
learn_na_percentage <- learn_merged %>%
  select(-all_of(learn_original_columns)) %>%  
  summarise(across(everything(), ~ as.integer(mean(is.na(.))*100))) %>%
  mutate(Statistics = "Learning set : percentage")  

# Test set : Number of NA for each column
test_na_count <- test_merged %>%
  select(-all_of(test_original_columns)) %>%  
  summarise(across(everything(), ~ as.integer(sum(is.na(.))))) %>%
  mutate(Statistics = "Test set : count")  # Addition of a column to indicate the stat

# Test set : % of NA for each colummn
test_na_percentage <- test_merged %>%
  select(-all_of(test_original_columns)) %>%  
  summarise(across(everything(), ~ as.integer(mean(is.na(.))*100))) %>%
  mutate(Statistics = "Test set : percentage") 

# Creation of the final table
na_sum_table <- bind_rows(learn_na_count, learn_na_percentage, test_na_count, test_na_percentage) %>% 
  relocate(Statistics, .before = everything())

print(na_sum_table)
```

## Descriptive Statistics

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}




```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
